%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Ayush Raj (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Ayush}{Raj}{ \urlstyle{same}\url{https://llucifer97.github.io/} \\
\href{mailto:ayushraj.bit17@gmail.com}{ayushraj.bit17@gmail.com} | Contact : (+91)7970761538
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\descript{Birla Institute Of Technology, MESRA }
\descript{BE in Electronics and communication engg.}
\location{CGPA 6.77}
\location{Expected MAY 2021 | India }

\section{} 

\descript{Delhi Public School ,Dhanbad }
\location{Class X - 9.8 Cgpa [ 2013-14 ]}
\location{Class XII - 80.2 Percentage [ 2015-16]}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github:// \href{https://github.com/llucifer97}{\custombold{llucifer97}} \\
LinkedIn://  \href{https://www.linkedin.com/in/ayush-raj97/}{\custombold{ayushraj97}} \\
Leetcode://  \href{https://leetcode.com/llucifer97/}{\custombold{llucifer97}}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\runsubsection{Programming}\\
 \textbullet{} C++ \textbullet{} Javascript \\
  \textbullet{} Python \textbullet{}  HTML5 \\ \textbullet{}CSS 
   \\
%\subsection{Programming}

\location{Frameworks/Libraries:}
 \textbullet{} MySQL 
\textbullet{}Express.js  \\ \textbullet{} Node.js
\textbullet{} React.js\\  
 
 
 \location{Tools/Software:}
 \textbullet{} GIT \textbullet{}Linux \textbullet{}Postman
\sectionsep


\section{COURSEWORK}
\textbullet{}Fundamentals of Data Structures\\
\textbullet{}Data structure and Algorithm (C++) \\
\textbullet{}Competitive Programming\\
\textbullet{}Operating Systems\\
\textbullet{}Computer Networks\\
\textbullet{}Object Oriented Programming\\
\textbullet{}Database Management Systems\\
%\subsection{Programming}







 \section{Soft Skills}
 \textbullet{}Strategic Thinking and Planning\\
\textbullet{}Ability to adapt to situations\\
 \textbullet{}Decision making
 \sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{Redhenlab}
\descript{| Google Summer Of Code’19 Student (open source)}
\location{Expected May 2019 – Aug 2019 | Remote}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}\item Planned,designed and developed a Gesture Annotator Tool to visualize and
validate human-pose extracted from  images , with over 2000+ lines of the codebase.
\item Developed the UI and integrated the plotting features and integrated with RESTAPI and deployed in singularity container on Redhen cloud server.
\item Wrote web-crawler to collect GBs of data from open sources and bash scripts
to automate the ML pipeline.
\item Project can be found  \href{https://summerofcode.withgoogle.com/archive/2019/projects/5565179075493888/}{Here}.
\item Tech stack: Flask ,Python ,MongoDB, keras
\end{tightemize}
\sectionsep

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Project
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{PROJECTS}

\runsubsection{GEEKCHAT}
\descript{| \href{https://geeky-chat.herokuapp.com}{Demo} }

GeekChat is an realtime multiuser chat app,to enable real-time, bidirectional communication
\begin{tightemize}
\item Provides a Global Chat which can be used by anyone using the application to
broadcast messages to everyone else in the particular room.
\item Updates conversation lists, user lists and messages in real time.
\item Tech stack: HTML , CSS ,socket.io , Node.js
\end{tightemize}
\sectionsep

\runsubsection{VIPANI}
\descript{| \href{https://github.com/llucifer97/Vipani}{code}}

Vipani is an online e-commerce web app to serve its customer products online.
\begin{tightemize}
\item Build a Restful APIs and created endpoints to perform CRUD operations.
\item Designed and implemented database schema in MongoDB for data storage .
\item Tech stack: Node.js , JavaScript , Express, React.js , MongoDB
\end{tightemize}
\sectionsep

\runsubsection{DataStore}
\descript{| \href{https://github.com/llucifer97/Data-Store}{code}}


\begin{tightemize}
\item It is file-based key-value datastore that supports CRUD operations used as
local storage for one single process.
\item Implemented TTL(time-to-live) cache for quick access of data.
\item Tech stack: Node.js , JavaScript , Express
\end{tightemize}
\sectionsep



\runsubsection{ACCOUNTING MANAGEMENT SYSTEM}
\descript{| \href{https://github.com/llucifer97/PAYROLL-MANAGEMENT-SYSTEM}{code}}


\begin{tightemize}
\item  Developed an application using C++ and wrote 1000+ lines of code
\item  Used Object-oriented programming(OOP) concepts 
\item  Tech stack: C++14 
\end{tightemize}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{ACHIEVEMENTS} 
\begin{tabular}{rll}
2018	    & Got third position in Machine Learning Hacakthon(BIT MESRA)\\
2020        & Solved 600+ problems on various coding platforms\\
2021        & Cleared first round of Uber Hastag challenge
\end{tabular}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SOCIETIES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\end{minipage} 
\end{document}
